### 2018-05-05 papers/synth/encoding.tex
asd

\subsubsection{Fixing VTS by adding edges}
%
Now we will consider the case when we add new edges to VTS to satisfy the properties.
%
In the following, the pseudo-Boolean formula $\texttt{AddE}$ encodes
that at most $slimit$ new undeclared edges may be added in the VTS.
%
\texttt{FixedForEdge} encodes the parts of the VTS that are not allowed to change.
\begin{align*}
  &\texttt{AddE}(slimit) = \sum~\texttt{AbsentE} \leq slimit\\
  &\texttt{FixedForEdge} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
   & \quad\quad\quad\quad \lnot \Lor \texttt{AbsentELabel} \;\union\;
                    \texttt{AbsentNLabel} \;\union\;
                    \texttt{AbsentP}
\end{align*}
We put together the constraints and obtain the following formula $\texttt{SynthE}(slimit)$.
\begin{align*}
  & \texttt{SynthE}(slimit) =
       \texttt{Consistancy}\land \texttt{Property} \land
   \texttt{FixedForEdge} \land
  \texttt{AddE}(slimit)
  % \tag{SynthE}\label{eq:addedge1}
\end{align*}
As we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
$\texttt{Property}$ encodes the goal, and
the rest two are defined just above.
%
A satisfying model of $\texttt{SynthE}$ will make 
some of the edges in $\texttt{AbsentE}$ true such that~$\texttt{Property}$ is satisfied.
%
We limit the addition of the edges, since we look for a fix that require minimum number
of changes in the given VTS.
%
We start with $slimit = 1$ and grow one by one until $\texttt{SynthE}(slimit)$
becomes satisfiable.

>>>>

\subsubsection{Fixing VTS by adding edges}
%
Now we will consider the case when we add new edges to VTS to satisfy the properties.
%
In the following, the pseudo-Boolean formula $\texttt{AddE}$ encodes
that at most $slimit$ new undeclared edges may be added in the VTS.
%
\texttt{FixedForEdge} encodes the parts of the VTS that are not allowed to change.
\begin{align*}
  &\texttt{AddE}(slimit) = \sum~\texttt{AbsentE} \leq slimit\\
  &\texttt{FixedForEdge} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
   & \quad\quad\quad\quad \lnot \Lor \texttt{AbsentELabel} \;\union\;
                    \texttt{AbsentNLabel} \;\union\;
                    \texttt{AbsentP}
\end{align*}
We put together the constraints and obtain the following formula.
\begin{align*}
  & \texttt{SynthE}(slimit) =
       \texttt{Consistancy}\land \texttt{Property} \land
   \texttt{FixedForEdge} \land
  \texttt{AddE}(slimit)
  % \tag{SynthE}\label{eq:addedge1}
\end{align*}
Similar to what we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
$\texttt{Property}$\; encodes the goal, and
the rest two are defined just above.
%
A satisfying model of $\texttt{SynthE}$ will make 
some of the edges in $\texttt{AbsentE}$ true such that~$\texttt{Property}$ is satisfied.
%
We limit the addition of the edges, since we look for a fix that require minimum number
of changes in the given VTS.
%
We start with $slimit = 1$ and grow one by one until $\texttt{SynthE}(slimit)$
becomes satisfiable.
